Quantifying the home ground advantage with `hyper2` and `hyper3` objects

### 2025-02-13 inst/home_advantage.Rmd
consistentification

```{r scotmax}
(H <- home_away3(home_away_table(a,give=FALSE),RCLF3_lambda_max))  # o$maximum ~= 1.353
maxp(H,give=1)
```

@@

save(RCLF3_table,  RCLF3_max, RCLF3_lambda_max, file="RCLF.rda")
```

>>>>

```{r scotmax}
(H <- home_away3(home_away_table(a,give=FALSE),RCLF3_lambda_max))  # o$maximum ~= 1.353
maxp(H,give=1)
RCLF3 <- H
```

@@

save(RCLF3_table,  RCLF3, RCLF3_max, RCLF3_lambda_max, file="RCLF.rda")
```
